Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-11-20 inst/doc/nonparametric-bayes.Rmd
actual draft sent to steve/marc

We infer posterior distributions for the parameters of each model
in a Bayesian context using Gibbs sampling (implemented in R [@RTeam]
using jags, [@R2jags]).  We choose uninformative uniform priors for all
parameters (See Appendix, Figures S1-S3, and Table S1, and the R code
provided). One-step-ahead predictions of these model fits are shown in
Figure 1.

@@

Despite the similarities in model fits to the observed data, the
policies inferred under each model differ widely, as shown in Figure 3.
Policies are shown in terms of target escapement, $S_t$.  Under models
such as this a constant escapement policy is expected to be optimal
[@Reed1979], whereby population levels below a certain size $S$ are
unharvested, while above that size the harvest strategy aims to return the
population to $S$, resulting in the hockey-stick shaped policies shown.
Only the structurally correct model (Allen model) and the GP produce
policies close to the true optimum policy (where both the underlying
model structure and parameter values are known without error).

@@

The consequences of managing 100 replicate realizations of the simulated
fishery under each of the policies estimated is shown in Figure 4.
As expected from the policy curves, the structurally correct model
under-harvests, leaving the stock to vary around it's un-fished optimum.
The structurally incorrect Ricker model over-harvests the population
passed the tipping point consistently, resulting in the immediate crash
of the stock and thus derives minimal profits.

These results are robust across a range of stochastic realizations,
models, and parameter values.  The results across this range can most
easily be compared by using the relative differences in net present
value realized by each of the model, as shown in Figure 5.  The BNP-SDP
approach most consistently realizes a value close to the optimal solution,
and importantly avoids ever driving the system across the tipping point,
which results in the near-zero value cases in the parametric models.

@@

These results are not sensitive to the modeling details of the simulation.  The BNP-SDP estimate remains very close to the optimal solution obtained by knowning the true model across changes to the training simulation, noise scale, parameters or structure of the underlying model, as seen in the figure. Results are pooled across different random seeds (111, 222, 333), noise values of 0.01 and 0.05 (not large enough to violate the self-sustaining criterion of @Reed1979), and different randomly generated parameters sets for each model, and using either the Myers or Allen as the underlying structure.  While the BNP-SDP performs slightly closer to optimal on the smaller noise levels, and closer on the Allen model then the Myers model, the differences are small compared to the values observed in using the wrong parametric model.  The BNP-SDP solution consistently avoids either failing to harvest at all or crashing the stock, which results in the very low profits/values seen in parametric models in the previous figure.

![Sensitivity Analysis](figure/sensitivity.pdf)

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2Jags] (see provided code).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, $\theta$ controls the strength of the nonlinearity, exhibiting an allee effect for $\theta \geq 2$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2Jags] (see code provided).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, allee threshold $C$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2Jags] (see code provided).

>>>>

We infer posterior distributions for the parameters of each model
in a Bayesian context using Gibbs sampling (implemented in R [@RTeam]
using jags, [@R2jags]).  We choose uninformative uniform priors for all
parameters (See Appendix, Figures and tables, and the R code
provided). One-step-ahead predictions of these model fits are shown in
Figure 1.  While alternative approaches to the estimation of the posteriors
(such as integrating out the rate parameter $r$ analytically and then
performing a grid search over the remaining parameter space), the 
approach of using a standard Gibbs sampler routine is both more general
and representitive of common practice in estimating posteriors for such models. 
Each sampling is tested for Gelman-Rubin convergence and results are robust
to longer runs.

@@

Despite the similarities in model fits to the observed data, the
policies inferred under each model differ widely, as shown in Figure 4.
Policies are shown in terms of target escapement, $S_t$.  Under models
such as this a constant escapement policy is expected to be optimal
[@Reed1979], whereby population levels below a certain size $S$ are
unharvested, while above that size the harvest strategy aims to return the
population to $S$, resulting in the hockey-stick shaped policies shown.
Only the structurally correct model (Allen model) and the GP produce
policies close to the true optimum policy (where both the underlying
model structure and parameter values are known without error).

@@

The consequences of managing 100 replicate realizations of the simulated
fishery under each of the policies estimated is shown in Figure 5.
As expected from the policy curves, the structurally correct model
under-harvests, leaving the stock to vary around it's un-fished optimum.
The structurally incorrect Ricker model over-harvests the population
passed the tipping point consistently, resulting in the immediate crash
of the stock and thus derives minimal profits.

These results are robust across a range of stochastic realizations,
models, and parameter values.  The results across this range can most
easily be compared by using the relative differences in net present
value realized by each of the model. Figure 6 shows the distribution of values
(profits) realized by each simulation shown in Figure 5.  The BNP-SDP
approach most consistently realizes a value close to the optimal solution,
and importantly avoids ever driving the system across the tipping point,
which results in the near-zero value cases in the parametric models.

@@

These results are not sensitive to the modeling details of the simulation.  The BNP-SDP estimate remains very close to the optimal solution obtained by knowning the true model across changes to the training simulation, noise scale, parameters or structure of the underlying model, as seen in Figure 7. Results are pooled across different random seeds (111, 222, 333), noise values of 0.01 and 0.05 (not large enough to violate the self-sustaining criterion of @Reed1979), and different randomly generated parameters sets for each model, and using either the Myers or Allen as the underlying structure.  While the BNP-SDP performs slightly closer to optimal on the smaller noise levels, and closer on the Allen model then the Myers model, the differences are small compared to the values observed in using the wrong parametric model.  The BNP-SDP solution consistently avoids either failing to harvest at all or crashing the stock, which results in the very low profits/values seen in parametric models in the previous figure. The sensitivity analysis is compared against the optimal solution alone and not shown against the estimates of the various parameteric models (but see Figure 6), where convergence of the Gibbs sampling could contribute to their poorer performance if not checked by hand for each configuration.

![Sensitivity Analysis.  Histogram shows the ratio of the realized net present value / profits derived when managing under the BNP-SDP Gaussian Process approach over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels.](figure/sensitivity.pdf)

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2jags] (see provided code).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, $\theta$ controls the strength of the nonlinearity, exhibiting an allee effect for $\theta \geq 2$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2jags] (see code provided).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation $\sigma$, representing the stochastic growth, $X_t$ the stock size at time $t$, $S_t$ the escapement (unharvested population that will recruit in the following year, $S_t = X_t - h_t$).  We place uniform priors on the growth rate $r$, carrying capacity $K$, allee threshold $C$, and log-normal standard deviation parameter $\sigma$, over ranges given in Table 1. Posteriors are inferred by Gibbs sampling using Jags [@R2jags] (see code provided).

### 2013-11-20 inst/doc/nonparametric-bayes.tex
actual draft sent to steve/marc

We develop these concerns in the context of fisheries, though the
underlying challenges and methods are germane to many other conservation
and resource management problems. The economic value and ecological
concern have made marine fisheries the crucible for much of the founding
work (H. S. Gordon 1954; Reed 1979; May et al. 1979; Ludwig and Walters
1982) in managing ecosystems under uncertainty. Global trends (Worm et
al. 2006) and controversy (Hilborn 2007; Worm et al. 2009) have made
understanding these challenges all the more pressing.

Uncertainty enters the decision-making process at many levels: intrinsic
stochasticity in biological processes, measurements, and implementation
of policy (\emph{e.g.} Reed 1979; Clark and Kirkwood 1986; Roughgarden
and Smith 1996; Sethi et al. 2005), parameteric uncertainty (\emph{e.g.}
Ludwig and Walters 1982; Hilborn and Mangel 1997; McAllister 1998;
Schapaugh and Tyre 2013), and model or structural uncertainty
(\emph{e.g.} B. K. Williams 2001; Cressie et al. 2009; Athanassoglou and
Xepapadeas 2012). Of these, structural uncertainty incorporates the
least a priori knowledge or assumptions and is generally the hardest to
quantify. Typical approaches assume a weak notion of model uncertainty
in which the correct model (or reasonable approximation) of the dynamics
must be identified from among a handful of alternative models. Here we
consider an approach that addresses uncertainty at each of these levels
without assuming the dynamics follow a particular (i.e.~parametric)
structure.

\emph{Cut the next three paragraphs, since they are covered more
consisely in the above paragraph?}

@@

This difficult position of having neither the true model nor data that
covers the full range of possible states is unfortunately the rule more
than the exception. The potential concern of tipping points in
ecological dyanmics (Scheffer et al. 2001; Polasky et al. 2011) reflects
these concerns -- as either knowledge of the true model or more complete
sampling of the state space would make it easy to identify if a tipping
point existed. If we do not know but cannot rule out such a possibility,
then we face decision-making under this dual challege of model
uncertainty and incomplete data coverage.

@@

This non-parametric property -- having a structure explicitly dependent
on the data -- is precisely the property that makes this approach
attractive in face of the limited data sampling challenges discussed
above. Having fit a parametric model to some data, the model is
completely described by the values (or posterior distributions) of it's
parameters. The non-parametric model is not captured by its parameter
values or distributions alone. Either the model scales with the
complexity of the data on which it is estimated (e.g.~nonparametric
heirarchical approaches such as the Dirchlet process) or the data points
become themselves part of the model specification, as in the
nonparametric regression used here.

@@

The posterior distribution for the hyper-parameters of the Gaussian
process model are estimated by Metropolis-Hastings algorithm, again with
details and code provided in the Appendix. Rasmussen and Williams (2006)
provides an excellent general introduction to Gaussian Processes and
Munch et al. (2005) first discusses their application in the context of
population dynamics models such as fisheries stock-recruitment
relationships.

@@

We introduce parameteric uncertainty by first estimating each of the
candidate models from data on unexploited stock dynamics following some
pertubation (non-equilibrium initial condition) over several time steps.
This training data could be generated in several different ways (such as
known variable exploitation rates, etc), as long as it reflects the
dynamics in some limited region of state space without impacting the
problem. We consider a period of 40 years of training data: long enough
that the estimates are not dependent on the particular realization,
while longer times are not likely to provide substantial improvement
(i.e.~the results are not sensitive to this interval). Each of the
models (described below) is fit to the same training data, as shown in
Figure 1.

We infer posterior distributions for the parameters of each model in a
Bayesian context using Gibbs sampling (implemented in R (Team 2013)
using jags, (Su and Yajima 2013)). We choose uninformative uniform
priors for all parameters (See Appendix, Figures S1-S3, and Table S1,
and the R code provided). One-step-ahead predictions of these model fits
are shown in Figure 1.

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/nonparametric-bayes-out_of_sample_predictions.pdf}
\caption{Out of sample predictions of the dynamics under each model.
Points show the stock size simulated by the true model. Overlay shows
the range of states predicted by each model, based on the state observed
in the previous time step. The Ricker model always predicts population
growth, while the actual population shrinks in each step as the initial
condition falls below the Allee threshold of the underlying model
(Allen). Note that the GP is both more pessimistic and more uncertain
about the future state than the parameteric models, while the realized
state often falls outside of the expected range forecasted by the
structurally incorrect Myers and Ricker models.}
\end{figure}

@@

Despite the similarities in model fits to the observed data, the
policies inferred under each model differ widely, as shown in Figure 3.
Policies are shown in terms of target escapement, $S_t$. Under models
such as this a constant escapement policy is expected to be optimal
(Reed 1979), whereby population levels below a certain size $S$ are
unharvested, while above that size the harvest strategy aims to return
the population to $S$, resulting in the hockey-stick shaped policies
shown. Only the structurally correct model (Allen model) and the GP
produce policies close to the true optimum policy (where both the
underlying model structure and parameter values are known without
error).

@@

These results are not sensitive to the modeling details of the
simulation. The BNP-SDP estimate remains very close to the optimal
solution obtained by knowning the true model across changes to the
training simulation, noise scale, parameters or structure of the
underlying model, as seen in the figure. Results are pooled across
different random seeds (111, 222, 333), noise values of 0.01 and 0.05
(not large enough to violate the self-sustaining criterion of Reed
(1979)), and different randomly generated parameters sets for each
model, and using either the Myers or Allen as the underlying structure.
While the BNP-SDP performs slightly closer to optimal on the smaller
noise levels, and closer on the Allen model then the Myers model, the
differences are small compared to the values observed in using the wrong
parameteric model. The BNP-SDP solution consistently avoids either
failing to harvest at all or crashing the stock, which results in the
very low profits/values seen in parameteric models in the previous
figure.

\begin{figure}[htbp]
\centering
\includegraphics{figure/sensitivity.pdf}
\caption{Sensitivity Analysis}
\end{figure}

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, and log-normal standard
deviation parameter $\sigma$, over ranges given in Table 1. Posteriors
are inferred by Gibbs sampling using Jags ({\textbf{???}}) (see provided
code).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, $\theta$ controls the
strength of the nonlinearity, exhibiting an allee effect for
$\theta \geq 2$, and log-normal standard deviation parameter $\sigma$,
over ranges given in Table 1. Posteriors are inferred by Gibbs sampling
using Jags ({\textbf{???}}) (see code provided).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, allee threshold $C$, and
log-normal standard deviation parameter $\sigma$, over ranges given in
Table 1. Posteriors are inferred by Gibbs sampling using Jags
({\textbf{???}}) (see code provided).

>>>>

We develop a novel approach to address these concerns in the context of
fisheries; though the underlying challenges and methods are germane to
many other conservation and resource management problems. The economic
value and ecological concern have made marine fisheries the crucible for
much of the founding work (H. S. Gordon 1954; Reed 1979; May et al.
1979; Ludwig and Walters 1982) in managing ecosystems under uncertainty.
Global trends (Worm et al. 2006) and controversy (Hilborn 2007; Worm et
al. 2009) have made understanding these challenges all the more
pressing.

Uncertainty enters the decision-making process at many levels: intrinsic
stochasticity in biological processes, measurements, and implementation
of policy (\emph{e.g.} Reed 1979; Clark and Kirkwood 1986; Roughgarden
and Smith 1996; Sethi et al. 2005), parametric uncertainty (\emph{e.g.}
Ludwig and Walters 1982; Hilborn and Mangel 1997; McAllister 1998;
Schapaugh and Tyre 2013), and model or structural uncertainty
(\emph{e.g.} B. K. Williams 2001; Cressie et al. 2009; Athanassoglou and
Xepapadeas 2012). Of these, structural uncertainty incorporates the
least a priori knowledge or assumptions and is generally the hardest to
quantify. Typical approaches assume a weak notion of model uncertainty
in which the correct model (or reasonable approximation) of the dynamics
must be identified from among a handful of alternative models. Here we
consider an approach that addresses uncertainty at each of these levels
without assuming the dynamics follow a particular (i.e.~parametric)
structure.

\emph{Cut the next three paragraphs, since they are covered more
concisely in the above paragraph?}

@@

This difficult position of having neither the true model nor data that
covers the full range of possible states is unfortunately the rule more
than the exception. The potential concern of tipping points in
ecological dynamics (Scheffer et al. 2001; Polasky et al. 2011) reflects
these concerns -- as either knowledge of the true model or more complete
sampling of the state space would make it easy to identify if a tipping
point existed. If we do not know but cannot rule out such a possibility,
then we face decision-making under this dual challege of model
uncertainty and incomplete data coverage.

@@

This non-parametric property -- having a structure explicitly dependent
on the data -- is precisely the property that makes this approach
attractive in face of the limited data sampling challenges discussed
above. Having fit a parametric model to some data, the model is
completely described by the values (or posterior distributions) of it's
parameters. The non-parametric model is not captured by its parameter
values or distributions alone. Either the model scales with the
complexity of the data on which it is estimated (e.g.~nonparametric
hierarchical approaches such as the Dirchlet process) or the data points
become themselves part of the model specification, as in the
nonparametric regression used here.

@@

The posterior distribution for the hyper-parameters of the Gaussian
process model are estimated by Metropolis-Hastings algorithm, again with
details and code provided in the Appendix. Rasmussen and Williams (2006)
provides an excellent general introduction to Gaussian Processes and
Munch, Kottas, and Mangel (2005) first discusses their application in
the context of population dynamics models such as fisheries
stock-recruitment relationships.

@@

We introduce parametric uncertainty by first estimating each of the
candidate models from data on unexploited stock dynamics following some
perturbation (non-equilibrium initial condition) over several time
steps. This training data could be generated in several different ways
(such as known variable exploitation rates, etc.), as long as it
reflects the dynamics in some limited region of state space without
impacting the problem. We consider a period of 40 years of training
data: long enough that the estimates are not dependent on the particular
realization, while longer times are not likely to provide substantial
improvement (i.e.~the results are not sensitive to this interval). Each
of the models (described below) is fit to the same training data, as
shown in Figure 1.

We infer posterior distributions for the parameters of each model in a
Bayesian context using Gibbs sampling (implemented in R (Team 2013)
using jags, (Su and Yajima 2013)). We choose uninformative uniform
priors for all parameters (See Appendix, Figures and tables, and the R
code provided). One-step-ahead predictions of these model fits are shown
in Figure 1. While alternative approaches to the estimation of the
posteriors (such as integrating out the rate parameter $r$ analytically
and then performing a grid search over the remaining parameter space),
the approach of using a standard Gibbs sampler routine is both more
general and representitive of common practice in estimating posteriors
for such models. Each sampling is tested for Gelman-Rubin convergence
and results are robust to longer runs.

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/nonparametric-bayes-out_of_sample_predictions.pdf}
\caption{Out of sample predictions of the dynamics under each model.
Points show the stock size simulated by the true model. Overlay shows
the range of states predicted by each model, based on the state observed
in the previous time step. The Ricker model always predicts population
growth, while the actual population shrinks in each step as the initial
condition falls below the Allee threshold of the underlying model
(Allen). Note that the GP is both more pessimistic and more uncertain
about the future state than the paramteric models, while the realized
state often falls outside of the expected range forecast by the
structurally incorrect Myers and Ricker models.}
\end{figure}

@@

Despite the similarities in model fits to the observed data, the
policies inferred under each model differ widely, as shown in Figure 4.
Policies are shown in terms of target escapement, $S_t$. Under models
such as this a constant escapement policy is expected to be optimal
(Reed 1979), whereby population levels below a certain size $S$ are
unharvested, while above that size the harvest strategy aims to return
the population to $S$, resulting in the hockey-stick shaped policies
shown. Only the structurally correct model (Allen model) and the GP
produce policies close to the true optimum policy (where both the
underlying model structure and parameter values are known without
error).

@@

These results are not sensitive to the modeling details of the
simulation. The BNP-SDP estimate remains very close to the optimal
solution obtained by knowning the true model across changes to the
training simulation, noise scale, parameters or structure of the
underlying model, as seen in Figure 7. Results are pooled across
different random seeds (111, 222, 333), noise values of 0.01 and 0.05
(not large enough to violate the self-sustaining criterion of Reed
(1979)), and different randomly generated parameters sets for each
model, and using either the Myers or Allen as the underlying structure.
While the BNP-SDP performs slightly closer to optimal on the smaller
noise levels, and closer on the Allen model then the Myers model, the
differences are small compared to the values observed in using the wrong
parametric model. The BNP-SDP solution consistently avoids either
failing to harvest at all or crashing the stock, which results in the
very low profits/values seen in parametric models in the previous
figure. The sensitivity analysis is compared against the optimal
solution alone and not shown against the estimates of the various
parameteric models (but see Figure 6), where convergence of the Gibbs
sampling could contribute to their poorer performance if not checked by
hand for each configuration.

\begin{figure}[htbp]
\centering
\includegraphics{figure/sensitivity.pdf}
\caption{Sensitivity Analysis. Histogram shows the ratio of the realized
net present value / profits derived when managing under the BNP-SDP
Gaussian Process approach over the optimal value given the true model
and true parameters. Values near 1 indicate nearly optimal performance.
Simulations cover a range of underlying parameter, model, replicate, and
noise levels.}
\end{figure}

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, and log-normal standard
deviation parameter $\sigma$, over ranges given in Table 1. Posteriors
are inferred by Gibbs sampling using Jags (Su and Yajima 2013) (see
provided code).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, $\theta$ controls the
strength of the nonlinearity, exhibiting an allee effect for
$\theta \geq 2$, and log-normal standard deviation parameter $\sigma$,
over ranges given in Table 1. Posteriors are inferred by Gibbs sampling
using Jags (Su and Yajima 2013) (see code provided).

@@

where $Z_t$ is log-normal noise of mean unity and log standard deviation
$\sigma$, representing the stochastic growth, $X_t$ the stock size at
time $t$, $S_t$ the escapement (unharvested population that will recruit
in the following year, $S_t = X_t - h_t$). We place uniform priors on
the growth rate $r$, carrying capacity $K$, allee threshold $C$, and
log-normal standard deviation parameter $\sigma$, over ranges given in
Table 1. Posteriors are inferred by Gibbs sampling using Jags (Su and
Yajima 2013) (see code provided).
